An Open System for\\ Managing Short Programming Exercises

### 2013-08-12 paper/talk.tex
clarifications/simplifications
questions about classification/ranking

\begin{itemize}
  \item There are lots of programming exercise systems already:
  \begin{itemize}
    \item Free: CodingBat, PracticeIt!, Codecademy
    \item Commercial: CodeLab (TuringsCraft), MyProgrammingLab (Pearson)
    \item {\em Do we really need another one?}
  \end{itemize}
  \item We did not know of one that
  \begin{itemize}
    \item Encouraged users to create and share {\bf freely-redistributable} exercises
    \item Supported a range of languages (including C/C++)
    \item Was open source
    \item Collected rich data about how students work
  \end{itemize}
  \item We created a new system, called CloudCoder, to fill this niche
    \begin{itemize}
    \item \url{http://cloudcoder.org}
    \end{itemize}
\end{itemize}

@@

\begin{itemize}
  \item Open source (AGPL v3)
  \item Supports exercises in Java, Python, Ruby, and C/C++
  \item Web-based user interface
    \begin{itemize}
    \item 100\% HTML/CSS/JavaScript, no plugin required
    \end{itemize}
  \item Repository of freely-redistributable (CC-BY-SA) exercises:
        \url{https://cloudcoder.org/repo}
    \begin{itemize}
    \item We encourage users to contribute, but do not require them to
    \end{itemize}
  \item Collects fine-grained edit sequence of each student's work
\end{itemize}

@@

\begin{itemize}
  %\item The impact of a pedagogical technique or curriculum resource
  %      depends on how many students can access it
  \item Goal: make programming exercises available to {\bf anyone} at {\bf any time} for {\bf any purpose}
  \begin{itemize}
    \item No payment
    \item No restrictive licenses
    \item No central control
  \end{itemize}
  \item Exercises can be used in many contexts:
  \begin{itemize}
    \item Our need: assign exercises in the context of a course
    \item In-class exercises to support peer instruction
          (PCRS, Zingaro et.\ al., SIGCSE 2013)
      \begin{itemize}
      \item Summer 2013: PCRS can import exercises from the CloudCoder exercise repository!
      \end{itemize}
    \item Codecademy-style self-learning?
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
\item Are short exercises useful?
  \begin{itemize}
  \item Do you use short exercises in your courses currently?
    \begin{itemize}
    \item If so, how?
    \item If not, would you be interested in starting to use them?
    \end{itemize}
  \item What experiments should we do to measure effect on outcomes?
  \end{itemize}
\item How to incorporate short exercises into a course most effectively?
  \begin{itemize}
  \item How do we know what exercises should be assigned?
  \item In what order should the exercises be assigned?
  \item What mix of short exercises vs.\ larger assignments?
  \item How to motivate students to attempt exercises?
    \begin{itemize}
    \item Should they be graded?
    \end{itemize}
  \end{itemize}
\end{itemize}

>>>>

\begin{itemize}
  \item There are lots of programming exercise systems already:
  \begin{itemize}
    \item Free: CodingBat, PracticeIt!, Codecademy
    \item Commercial: CodeLab (TuringsCraft), MyProgrammingLab (Pearson)
    \item {\em Do we really need another one?}
  \end{itemize}
  \item We did not know of one that
  \begin{itemize}
    \item Encouraged users to create and share {\bf freely-redistributable} exercises
    \item Was open source
    \item Supported a range of languages (including C/C++)
    \item Collected rich data about how students work
  \end{itemize}
  \item We created a new system, called CloudCoder, to fill this niche
    \begin{itemize}
    \item \url{http://cloudcoder.org}
    \end{itemize}
\end{itemize}

@@

\begin{itemize}
  \item Open source (AGPL v3)
  \item Supports Java, Python, Ruby, and C/C++
  \item Repository of freely-redistributable (CC-BY-SA) exercises:
        \url{https://cloudcoder.org/repo}
    \begin{itemize}
    \item We encourage users to contribute, but do not require them to
    \end{itemize}
  \item Web-based user interface
    \begin{itemize}
    \item 100\% HTML/CSS/JavaScript, no plugin required
    \end{itemize}
  \item Collects fine-grained edit sequence of each student's work
\end{itemize}

@@

\begin{itemize}
  %\item The impact of a pedagogical technique or curriculum resource
  %      depends on how many students can access it
  \item Goal: make programming exercises available to {\bf anyone} at {\bf any time} for {\bf any purpose}
  \begin{itemize}
    \item No payment
    \item No restrictive licenses
    \item No central control
  \end{itemize}
  \item Exercises can be used in many contexts:
  \begin{itemize}
    \item Our need: assign exercises in the context of a course
    \item In-class exercises to support peer instruction
          (PCRS, Zingaro et.\ al., SIGCSE 2013)
      %\begin{itemize}
      %\item Summer 2013: PCRS can import exercises from the CloudCoder exercise repository!
      %\end{itemize}
    \item Codecademy-style self-learning?
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
\item Are short exercises useful?
  \begin{itemize}
  \item Do you use short exercises in your courses currently?
    \begin{itemize}
    \item If so, how?
    \item If not, would you be interested in starting to use them?
    \end{itemize}
  \item What experiments should we do to measure effect on outcomes?
  \end{itemize}
\item How do we classify exercises?
\item How do we rank exercises?
\item How to incorporate short exercises into a course most effectively?
  \begin{itemize}
  \item What exercises should be assigned? In what order?
  \item What mix of short exercises vs.\ larger assignments?
  \item How to motivate students to attempt them?
    \begin{itemize}
    \item Should they be graded?
    \end{itemize}
  \end{itemize}
\end{itemize}
